Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-26 latex/article.tex
redid last figure

 \begin{figure}[h!]
   \vspace{-0.35cm}
   \begin{center}
   	 {\includegraphics[width=0.45\textwidth]{figs/snow_r10}}
     {\includegraphics[width=0.5\textwidth]{figs/snow2_r10}}
     {\includegraphics[width=0.6\textwidth]{figs/xyzrgb_dragon-510_R8_mean}}
   \end{center}
   \caption{\emph{First row}: Mean curvature estimation on Snow Microstructures with a digital domain of $233^3$ and a radius of 10. 
   (left) Full snow object (right) exploration within the object
  \emph{Second row:} Mean curvature estimation on XYZ Dragon with a digital domain of $510^3$ and a radius of 8.}
   \label{fig:adaptive}
   \vspace{-0.35cm}
 \end{figure}

>>>>

 \begin{figure}[h!]
   \vspace{-0.35cm}
   \begin{center}
   	 {\includegraphics[width=0.4\textwidth]{figs/snow_r8}}
   	 {\includegraphics[width=0.4\textwidth]{figs/xyzrgb_dragon-510_R8_mean}}

     {\includegraphics[width=0.4\textwidth]{figs/snow_r8_min}}
	 {\includegraphics[width=0.4\textwidth]{figs/dragon_r8}}

     {\includegraphics[width=0.4\textwidth]{figs/snow_r8_max}}
	 {\includegraphics[width=0.4\textwidth]{figs/dragon_r8_max}}

     {\includegraphics[width=0.4\textwidth]{figs/snow_r8_normales}}
     {\includegraphics[width=0.4\textwidth]{figs/dragon_r8_normales}}

   \end{center}
   \caption{\emph{Left column}: Mean curvature, first and second principal directions and normales estimation on Snow Microstructures with a digital domain of $233^3$ and a radius of 8. 
  \emph{Right column:} Mean curvature, first and second principal directions and normales estimantion on XYZ Dragon with a digital domain of $510^3$ and a radius of 8.}
   \label{fig:adaptive}
   \vspace{-0.35cm}
 \end{figure}
